\thesistitle

### 2019-04-10 main.tex
Clone class

\documentclass{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}     % for proper word breaking at line ends
\usepackage[a4paper, total={170mm,250mm}]{geometry}
                                % for page size and margin settings
\usepackage{graphicx}           % for images
\usepackage{amsmath,amssymb}    % for better equations
\usepackage{amsthm}             % for better theorem styles
\usepackage{mathtools}          % for greek math symbol formatting
\usepackage{enumitem}           % for control of 'enumerate' numbering
\usepackage{listings}           % for control of 'itemize' spacing
\usepackage{todonotes}          % for clear TODO notes
\usepackage{hyperref}           % page numbers and '\ref's become clickable
\usepackage{titlesec}
\usepackage{csquotes}

@@

\chapter{Background}
\section{Clone Class}

@@

>>>>

\documentclass{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}     % for proper word breaking at line ends
\usepackage[a4paper, total={170mm,250mm}]{geometry}
                                % for page size and margin settings
\usepackage{graphicx}           % for images
\usepackage{amsmath,amssymb}    % for better equations
\usepackage{amsthm}             % for better theorem styles
\usepackage{mathtools}          % for greek math symbol formatting
\usepackage{enumitem}           % for control of 'enumerate' numbering
\usepackage{listings}           % for control of 'itemize' spacing
\usepackage{todonotes}          % for clear TODO notes
\usepackage{hyperref}           % page numbers and '\ref's become clickable
\usepackage{titlesec}
\usepackage{csquotes}
\usepackage{float}

@@

\chapter{Background}
\section{Clone Class}
Before we go into the refactoring of code clones, we must first define how we identify a clone. Roy \cite{roy2007survey} distinguishes clone pairs, clone classes and clone class families. For this thesis we will consider only ``clone classes'', as the other concepts do not add to the understanding and reasoning of clones as applied in this thesis. Roy defined ``clone classes'' as \textit{the union of all code portions/fragments which are identical or similar to each other}.

As an example, look at the code fragment displayed in figure \ref{fig:cloneclass}. It displays two clone classes. One clone class is in all three files, and has two lines in each file (line 5 and 6). The other clone class is only in the first two files, and has three lines in each file (line 5-7). The clone classes overlap partly.
\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-class}
	\caption{Simple example of two clone classes, one consisting of three blocks of code of three lines, one existing of two blocks of code of two lines.}
	\label{fig:cloneclass}
\end{figure}

@@

For this thesis, we have chosen not to further look at type III and IV clones, as it is very hard to formalize their refactoring processes. They are out of the scope for this thesis.
